\chapter{Fundamental Blocks of the Research} \label{chapter_two}


\section{Image Stabilisation}
What is image stabilisation?

% Start: Image Stabilisation
\subsection{Types of Image Stabilisation}
\subsubsection{Hardware Image Stabilisation}
Compensate camera movements with hardware. Expensive.

\subsubsection{Digital Image Stabilisation}
Compensate movements in post-processing. Economical.

\subsection{How Digital Image Stabilisation works}
We are interested in DIS so we will introduce the fundamentals.

% Start: IMU Sensors
\section{Inertial Measurement Unit Sensors}
\begin{itemize}
\item What are IMU Sensors?
\item What do they measure?
\item Applications?
\item Why use them for our application?
\item Advantages and Drawbacks
\end{itemize}

\subsection{Pose Estimation with IMUs}
How to measure pose with help of IMU Sensors?

\subsection{Noise Models}
About Noise in IMU Sensors

\subsection{Challenges in Working with IMU}
Various Challenges of working with IMUs.

% Start: Neural Networks
\section{Neural Network Architectures Explained}
We will be using a lot of Neural Networks. The basic functioning of them is explained here.

\subsection{Multi Layer Perceptron}
Most basic ANN.

\subsection{Convolutional Neural Networks}
More advanced neural networks.

\subsection{Recurrent Neural Networks}
Neural networks with memory.

\subsection{Attention Mechanism}
Talk about attention in Neural Networks.

\subsection{Transformer Networks}
How self attention is used in Neural Networks.
